Dark Control:\\ A Unified Account of Default Mode Function\\ by Control Theory and Reinforcement Learning

### 2017-04-24 paper/paper.tex
wip

% \subsubsection{Link to classical reinforcement learning algorithms}
% One should note that most classical RL algorithms, including \textit{Temporal Difference (TD)}
% learning \citep{sutton1998reinforcement}, REINFORCE \citep{williams1992}, and SARSA can be
% cast in this \textbf{please unpack the "this" here}
% general variational framework. For instance, TD corresponds to
% the above framework using a linear value approximator with feature encoding
% $\phi(s,a) = \delta_{(s,a)} =  \text{ point mass at }(s,a)$ on the grid
% $\mathcal S \times \mathcal A$, and so
% $$\nabla_{\theta}\tilde{Q}(s, a|\theta) = \phi(s, a) = \delta_{(s,a)}.$$
% Whence, the gradient update due to the sample $(s,a,r,s') \in \mathcal D$ is
% $$\theta(s,a) \leftarrow \theta(s,a) + \alpha(\tilde{Q}(s, a|\theta) - y),$$
% the well-known TD update rule \citep{sutton1998reinforcement}.

>>>>

\subsubsection{Link to classical reinforcement learning algorithms}
One should note that most classical RL algorithms, including \textit{Temporal Difference (TD)}
learning \citep{sutton1998reinforcement}, REINFORCE \citep{williams1992}, and SARSA can be
cast in this \textbf{please unpack the "this" here}
general variational framework. For instance, TD corresponds to
the above framework using a linear value approximator with feature encoding
$\phi(s,a) = \delta_{(s,a)} =  \text{ point mass at }(s,a)$ on the grid
$\mathcal S \times \mathcal A$, and so
$$\nabla_{\theta}\tilde{Q}(s, a|\theta) = \phi(s, a) = \delta_{(s,a)}.$$
Whence, the gradient update due to the sample $(s,a,r,s') \in \mathcal D$ is
$$\tilde{Q}(s, a) \leftarrow \tilde{Q}(s, a) + \alpha(y-\tilde{Q}(s, a)),$$
the well-known TD update rule \citep{sutton1998reinforcement}.
